### 2015-06-27 reports/paper/introduction.tex
thesis update

\section{Contribution}
In this thesis, we provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. We also demonstrated that our system can be used as a tool for painting in space.

We first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

\section{Contribution}
The main contributions of the thesis are:
\begin{enumerate}
\item We provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. 
\item We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. 
\item We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. 
\end{enumerate}
As a fun demonstration of the technology, we also demonstrated that our system can be used as a tool for painting in space.

\section{Outline}
We first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.
